Introducing Distributed Dynamic Data-intensive (D3) Science: Understanding Applications and Infrastructure

### 2016-08-20 3dpas_intro.tex
consistent spelling of loosely coupled

The second application factor that determines distribution of data is
the type of separation and coupling of the components of the
distributed application. Different coupling types place different
constraints on data distribution, either due to latency, or due to
data volumes that must be coordinated. % Different types of coupling in
% turn influences the distribution of data.
\emph{Loosely-coupled} distribution involves coordination and
cooperation between largely independent application components, as
might be found in a workflow system. \emph{Tightly-coupled}
applications involve greater constraints between the components,
either in latency tolerance, coordination requirements or relative
scheduling. \emph{Decoupled} distribution results in the separation of
application components elements of the same task, for example, sharing
a spatial data set between components that cooperate to perform a
single logical task~\cite{dpa_surveypaper}.
% thebookthatchangedtheworld
Most of the applications in \S\ref{sec:scenarios} are loosely coupled,
with the CMB (\S\ref{astroJulian}) and Fusion (\S\ref{fusionScott})
applications as examples of tight coupling.

@@

The {\em MapReduce} paradigm~\cite{MapReduce} and its variants~\cite{twister,hmr} are the most prominent among the bulk data-parallel frameworks which use bulk operators to express computations over collections of data in an loosely coupled manner.  Applications such as Next Generation Sequencing (NGS) (\S\ref{bioSilvia}) and Power Grids (\S\ref{power}) use MapReduce for
their analytics~\cite{cloudburst,genometoolkit,Yin:mapreduce:2012}.

>>>>

The second application factor that determines distribution of data is
the type of separation and coupling of the components of the
distributed application. Different coupling types place different
constraints on data distribution, either due to latency, or due to
data volumes that must be coordinated. % Different types of coupling in
% turn influences the distribution of data.
\emph{Loosely-coupled} distribution involves coordination and
cooperation between largely independent application components, as
might be found in a workflow system. \emph{Tightly-coupled}
applications involve greater constraints between the components,
either in latency tolerance, coordination requirements or relative
scheduling. \emph{Decoupled} distribution results in the separation of
application components elements of the same task, for example, sharing
a spatial data set between components that cooperate to perform a
single logical task~\cite{dpa_surveypaper}.
% thebookthatchangedtheworld
Most of the applications in \S\ref{sec:scenarios} are loosely-coupled,
with the CMB (\S\ref{astroJulian}) and Fusion (\S\ref{fusionScott})
applications as examples of tight coupling.

@@

The {\em MapReduce} paradigm~\cite{MapReduce} and its variants~\cite{twister,hmr} are the most prominent among the bulk data-parallel frameworks which use bulk operators to express computations over collections of data in an loosely-coupled manner.  Applications such as Next Generation Sequencing (NGS) (\S\ref{bioSilvia}) and Power Grids (\S\ref{power}) use MapReduce for
their analytics~\cite{cloudburst,genometoolkit,Yin:mapreduce:2012}.
